### 2018-03-11 Draft2/DataCollection.tex
Changes for NYCSEF finals round

To test my claims, I measured the performance of the above operations in a real programming language and runtime. My computing environment consisted of a Windows 10 desktop with an Intel Core i5-4460T 1.90GHz Haswell processor for the appending benchmarks, and a Windows 10 laptop with an Intel Core i5-7200U 2.50GHz Kaby Lake processor for the other benchmarks. On both computers, I used C\# 7.0 with the .NET Core 2.1.4 runtime. I used the excellent BenchmarkDotNet library to obtain performance metrics and plotted them with the R package ggplot2.

I compared the performance of a growth array implementation I had written in C\# to that of a heavily-optimized dynamic array that was part of the C\# standard library, \texttt{System.Collections.Generic.List}. The \texttt{List} type had parameters $\VarInitCapacity = 4$ and $\VarGrowthFactor = 2$, while my growth array implementation had $\VarInitCapacity = 8$ and $\VarGrowthFactor = 2$. (The different values of $\VarInitCapacity$ were not significant since $\frac{8}{4}$ was a multiple of $\VarGrowthFactor$, causing the two collections to exhibit similar trends for large $n$.) I used 57 unique values of $n$ for the appending benchmarks, and 15 different values of $n$ for the other benchmarks. In both cases, input values included increasing powers of $2$ up to $32768$. For the appending benchmarks, I also included numbers that were one more than a power of $2$, numbers that were the average of two consecutive powers of $2$, and all numbers less than $10$ in my input data. Here are my results:

@@

>>>>

To test my claims, I measured the performance of the above operations in a real programming language and runtime. My computing environment consisted of a Windows 10 desktop with an Intel Core i5-4460T 1.90GHz Haswell processor. I used C\# 7.0 with the .NET Core 2.1.4 runtime. I used the excellent BenchmarkDotNet library to obtain performance metrics and plotted them with the R package ggplot2.

I compared the performance of a growth array implementation I had written in C\# to that of a heavily-optimized dynamic array provided by the C\# standard library, \texttt{System.Collections.Generic.List}. The \texttt{List} type had parameters $\VarInitCapacity = 4$ and $\VarGrowthFactor = 2$, while my growth array implementation had $\VarInitCapacity = 8$ and $\VarGrowthFactor = 2$. (The different values of $\VarInitCapacity$ were not significant since $\frac{8}{4}$ was a multiple of $\VarGrowthFactor$, causing the two collections to exhibit similar trends for large $n$.) I used 57 unique values of $n$ for the appending benchmarks, and 15 different values of $n$ for the other benchmarks. In both cases, input values included increasing powers of $2$ up to $32768$. For the appending benchmarks, I also tested with values of $n$ that were one more than a power of $2$, values that were the average of two consecutive powers of $2$, and values from $1$ to $10$. Here are my results:

@@

For all benchmarks, BenchmarkDotNet consistently reported margins of error and standard deviation values on the order of $\frac{1}{100}$th of the measurement values.
